Honey Bee Colonies Impacted by Varroa, American Foulbrood and Global Warming

### 2024-08-02 starter-analysis-exercise/products/report/manuscript_final-2.qmd
update to personal website 08.02.24

#knitr::include_graphics(here("assets","antigen-recognition.png"))
```

@@

```{r}
# Descriptive Statistics
print("Descriptive Statistics:")
summary(data_clean)
str(data_clean)
```

>>>>

```{r}
# Install necessary packages
#install.packages("DiagrammeR")

# Load the DiagrammeR package
library(DiagrammeR)

# Create the flowchart using DiagrammeR
grViz("
  digraph Data_Analysis_Flowchart {
    graph [layout = dot, rankdir = TB]

    node [shape = box, style = filled, color = lightblue]

    Define_Objectives [label = 'Define Objectives']
    Collect_Data [label = 'Collect Data']
    Clean_Data [label = 'Clean Data']
    Analyze_Data [label = 'Analyze Data']
    Interpret_Results [label = 'Interpret Results']
    Visualize_Data [label = 'Visualize Data']
    Compile_Report [label = 'Compile Report']
    Review_Revise [label = 'Review & Revise']
    Present_Report [label = 'Present Report']

    Define_Objectives -> Collect_Data
    Collect_Data -> Clean_Data
    Clean_Data -> Analyze_Data
    Analyze_Data -> Interpret_Results
    Interpret_Results -> Visualize_Data
    Visualize_Data -> Compile_Report
    Compile_Report -> Review_Revise
    Review_Revise -> Present_Report
  }
")
```

![](/images/FlowChart.jpg){fig-align="center"}

@@

```{r}
# Descriptive Statistics
print("Descriptive Statistics:")
summary(data_clean)
